% draft of the paper, built on Sep.29 by Huo Xiaokai, Email: hxk12@mails.tsinghua.edu.cn
% Chang on Dec. 3
% Revised on Dec. 7
% this is a combination of Oldroydnew1 and Oldroyddecay
\documentclass{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{cite}
%\usepackage{showkeys}
\theoremstyle{plain}
\begin{document}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\theoremstyle{Remark}
\newtheorem{rem}{Remark}
\newtheorem{defn}{Definition}

\title{Structural stability of a 1D compressible viscoelastic fluid model}

\author{Xiaokai Huo \footnote{Zhou Pei-Yuan Center for Appl. Math., Tsinghua Univ., Beijing 100084, China; Email:
hxk12@mails.tsinghua.edu.cn},
~Wen-An Yong\footnote{Zhou Pei-Yuan Center for Appl. Math., Tsinghua Univ., Beijing 100084, China; Email:
Email: wayong@tsinghua.edu.cn}}

\date{}

\numberwithin{equation}{section}

\maketitle

\begin{abstract}

This paper is concerned with a compressible viscoelastic fluid model proposed by \"Ottinger.
%It consists of conservation laws (of mass and momentum) and a constitutive equation for a configuration tensor.
Although the model has a convex entropy, the Hessian matrix of the entropy does not symmetrize the system of first-order partial differential equations due to the non-conservative terms in the constitutive equation. We show that the corresponding 1D model is symmetrizable hyperbolic and dissipative and satisfies the Kawashima condition. Based on these, we prove the global existence of smooth solutions near equilibrium and justify the compatibility of the model with the Navier-Stokes equations.

\end{abstract}

\section{Introduction}

Complex fluids are ubiquitous in our daily life and in modern industry.
Examples include shampoo, toothpaste, silly putty, blood, polymeric solutions, emulsions, suspensions, liquid crystals, and glass-forming liquids.
When undergoing deformation, many of such materials exhibit both viscous and elastic characteristics and therefore
are often called viscoelastic fluids. The motion of such fluids is governed by conservation laws (of mass, momentum and energy) together with constitutive equations.
The constitutive equations, such as the Oldroyd-B and Upper-Convected Maxwell (UCM) models, link the stress in the conservation laws to the velocity field or strain and describe the viscoelastic characteristics. Most of the existing models are for dilute solutions or low-frequency mechanical responses, where the viscoelastic fluids can be well assumed to be incompressible. For incompressible models, many important mathematical results have been achieved. The interested reader is referred to \cite{larson1999structure,squires2009fluid,lin2012some,renardy2008mathematical} for what stated above.

%Since in viscoelastic fluids the viscous solvent is almost always incompressible, and the elastic components are also incompressible under low frequencies \cite{larson1999structure,squires2009fluid}, it is reasonable that the classical models take the incompressible assumptions on the velocity field.

However, recent studies show that the compressibility of viscoelastic fluids is non-negligible in many situations, such as high-frequency vibrations of nanoparticles immersed in viscoelastic fluids like water-glycerol mixtures \cite{yu2015compressible,galstyan2015note,chakraborty2015constitutive,pelton2009damping}, injecting/compression processes in plastic engineering \cite{kim1999numerical},
%polymeric melts,
and bubble collapses in compressible fluids \cite{lind2013bubble}.
%and on the hydrodynamics of polymeric melts \cite{housiadas2011perturbation} have attracted many interests in developing compressible models for the viscoelastic fluids. the vibrations of nanoscale mechanical devices in simple liquids.
%In these situations, the high-frequency vibration of nanoparticles and the high concentration of elastic components make the classical incompressible models invalid in describing the hydrodynamics of these fluids. In microrheology, the understanding of the compressibility effect of the elastic components on the flowing behavior is important \cite{squires2009fluid}. The compressibility effect is also vital in the other applications like understanding bubble dynamics \cite{lind2013bubble} and modeling injecting/compression process in plastic engineering \cite{kim1999numerical}.
Motivated  by these important applications, a number of compressible viscoelastic models have been developed over the past years. Most of them were derived by modifying the classical incompressible Oldroyd-B or UCM models \cite{beris2013thermodynamics,ottinger2005beyond,edwards1990remarks,belblidia2006stabilised,bollada2012mathematical,chakraborty2015constitutive,sureshkumar2004stability}. For example, that in \cite{edwards1990remarks} differs from the UCM model only by a term of the divergence of velocity field multiplying the stress. Those models often contain Oldroyd or other co-rotational derivatives to meet the principle of material indifference, which guarantees that the properties of the fluids are indifferent with the coordinate systems.
%Actually, according to \cite{bollada2012mathematical}, a widely accepted compressible model is not available.
%In \cite{bollada2012mathematical}, the models proposed in \cite{edwards1990remarks,beris2013thermodynamics,wilmanski2008continuum,belblidia2006stabilised} are discussed and a isothermal UCM like constitutive equations are derived.
%Among these models,  \cite{wilmanski2008continuum} adds a term with the contraction of stress tensor and velocity gradient tensor, and \cite{belblidia2006stabilised} decompose the stress into non-Newtonian polymeric parts and Newtonian solvent parts. In the model derived in \cite{bollada2012mathematical}, the dependence of viscosity on density is considered and a nonzero divergence of the velocity field is added in the constitutive equation.
In \cite{chakraborty2015constitutive}, the authors analyzed various compressible constitutive equations in the linear regime. They found that, except the model in \cite{yong2014newtonian}, all others do not capture the correct response in the high-frequency limit.
%One can actually apply a similar analysis on the models discussed in \cite{bollada2012mathematical} and find that they do not capture the high-frequency limit.
%with the Newtonian limit and high-frequency limit.
%Most of the models \cite{edwards1990remarks,sureshkumar2004stability,chakraborty2015constitutive} except the model proposed in \cite{yong2014newtonian} do not capture the proper response in the high-frequency limit.
But the model in \cite{yong2014newtonian} does not obey the material indifference principle.
In addition, a compressible model, using the deformation tensor instead of the stress tensor, was proposed in \cite{qian2010global,hu2011global} by generalizing the incompressible model \cite{lin2005hydrodynamics} through withdrawing the incompressibility assumption therein.
%evolution equations %in nonlinear continuum mechanics.
%intensively studied
Most of the compressible models mentioned above are isothermal and lack a thermodynamic basis.
%Unlike the thermodynamic considerations is largely avoided with the incompressibility assumption in the modeling of viscoelastic fluids, it is important in developing compressible viscoelastic fluid models. Most of the models derived from modifying the classical models \cite{edwards1990remarks,wilmanski2008continuum,belblidia2006stabilised,sureshkumar2004stability} or from the mathematical considerations \cite{qian2010global,hu2011global,yong2014newtonian}, do not take the temperature into consideration. And their consistencies with thermodynamic laws are not clear.
%It is expected that the constitutive equations should be derived from thermodynamic theories. Due to the non-conservative form of objective derivatives, the Posssion bracket formalism was not valid and a extended bracket formalism has been developed \cite{grmela1984bracket,morrison1984bracket,kaufman1984dissipative}.

On the other hand, with the GENERIC formalism for non-equilibrium thermodynamics \"Ottinger proposed a non-isothermal compressible model for complex fluids \cite{ottinger2005beyond}.
%applied the method in complex fluids \cite{grmela1997dynamicsI,ottinger1997dynamicsII,ottinger2005beyond}. It extends the Hamiltonian formalism for classical mechanics to general thermodynamic systems based on the second law of thermodynamics. Compared with the other models,
Different from the others, \"Ottinger's model uses an evolution equation for a configuration tensor and takes the stress as a function of the latter.
%The evolution equation contains and , a new configuration tensor is introduced with The Oldroyd derivative. And
It obeys both the principle of material indifference and the second law of thermodynamics.
%In a simple case without consideration of temperature,
In the isothermal case, the model reads as
\begin{subequations}\label{11}
  \begin{align}
  \partial_t \rho + \nabla \cdot (\rho \mathbf{v}) = 0, \\
  \partial_t (\rho \mathbf{v}) + \nabla \cdot (\rho \mathbf{v}\mathbf{v} + p) + \nabla \cdot \pi =0, \\
  \partial_t \mathbf{c} + \mathbf{v} \cdot \nabla \mathbf{c} + (\nabla \mathbf{v})  \mathbf{c }+ \mathbf{c}  (\nabla \mathbf{v})^T -(\nabla \mathbf{v} +(\nabla \mathbf{v})^T ) = -\frac{\mathbf{c}}{\tau}, \label{11-3}
\end{align}
\end{subequations}
where the first two equations are the standard conservation laws (of mass and momentum) and the third one is the constitutive equation for the configuration tensor $\mathbf{c}$.
In \eqref{11}, $\rho=\rho(x, t)$ is the fluid density, $\mathbf{v}$ is the velocity, $p=p(\rho)$ is the pressure, $\pi=2\mathbf{c} \cdot (\mathbf{c}-\mathbf{I})-\frac{1}{2}tr(\mathbf{c}^2)\mathbf{I}$ is the stress tensor with $\mathbf{I}$ the identity tensor, $tr(\mathbf{c}^2) = \sum_{i,j}c_{ij}c_{ji}$, $\nabla \mathbf{v}=[ \partial_{x_j} v_i]$, and $\tau$ is a relaxation time related to the viscosity of fluid. Notice that this model consists of only first-order partial differential equations and contains non-conservative terms in \eqref{11-3} due to the Oldroyd derivative.

The main goal of this paper is to study the structural stability of system \eqref{11} in one dimension:
\begin{subequations}\label{12}
  \begin{align}
  \partial_t \rho + \partial_x (\rho v) = 0 , \\
\partial_t (\rho v) + \partial_x (\rho v^2) + \partial_x p + (3c-2) \partial_x c = 0, \\
\partial_t c + v \partial_x c + (2c-2) \partial_x v =-\frac{c}{\tau}.
\end{align}
\end{subequations}
We show that this one-dimensional system is symmetrizable hyperbolic \cite{friedrichs1954symmetric} and dissipative in the sense of \cite{yong1992singular,yong1999singular} and satisfies the Kawashima condition \cite{kawashima1985systems}. With these nice properties,
we establish the global existence of small smooth solutions to the one-dimensional system and justify its compatibility with the Navier-Stokes equations.
%The global existence result is established with showing that this the compatibility with the Navier-Stokes equations is also rigorously justified.
We also show that, although the model \eqref{11} has a convex entropy, the Hessian of the entropy function does not symmetrize the system of
first-order partial differential equations due to the non-conservative terms. This is in contrast to the classical theory for hyperbolic conservation laws \cite{friedrichs1971systems} and explains why only the one-dimensional case is studied here.

Let us mention that there has been a substantial interest in the mathematical analysis of compressible viscoelastic fluids in recent years \cite{lei2006global,fang2014incompressible,hu2011global,qian2010global,hu2013global,hu2010local,qian2011initial, yong2014newtonian,guillope2010regular}. The non-conservative co-rotational derivatives
%and the inclusion of density equations
are the main difficulty. Most works are about the local and global existence of smooth solutions near equilibrium and the incompressible limit. In \cite{qian2010global,hu2011global, qian2011initial}, the authors established the local and global existence of smooth solutions in Besov spaces to the compressible model generalizing the incompressible one \cite{lin2005hydrodynamics}.
%The initial-boundary problem is investigated in \cite{qian2011initial}.
For a weakly compressible Oldroyd-B model, the local and global existence of smooth solutions were proved in \cite{guillope2010regular}.
On the other hand, the incompressible limit was justified in \cite{lei2006global,fang2014incompressible} for initial value problems of the Oldroyd-B model.
%Most of these work rewrites the equations in a hyperbolic-parabolic system with the non-conservative terms treated separately.
In addition, it was justified in \cite{yong2014newtonian} that a therein revised Maxwell model is compatible with the Navier-Stokes equations.
% by exploiting the conservation-dissipation property of the model.
%It is based on the fact the the system is a hyperbolic conservative balance system with entropy.

The paper is organized as follows. In the next section an entropy function for model (1.1) is discussed. We then show that the one-dimensional system (1.2) is symmetrizable hyperbolic and dissipative, and satisfies the Kawashima condition. The global existence result is established in Section 4. The last section is devoted to a proof of the compatibility with the Navier-Stokes equations.

%Complex fluids are prevalent in our daily life. Viscoelastic fluids cover a large content of complex fluids, including polymers, liquid crystals, electrorheological suspensions, glass-forming liquids, etc \cite{larson1999structure,lin2012some}.
%
%%The hydrodynamical and rheological properties interact in the flowing of the fluids, leading to various complex phenomena in the fluids.
%
%The motion of such fluids is governed by conservation laws of (mass, momentum and energy) and constitutive equations together \cite{oldroyd1950formulation}.
%
%Because of ?, most complex fluids are usually assumed to be incompressible. progress have been achieved in the past, both mathematically and . The interested reader is referred to for a comprehensive survey of the mathematical results.
%
%On the other hand,
%bubble dynamics
%in plastic engineering. A number of models have been developed over the past years. Most of them
%%Recently the study on the interactions between viscoelastic fluids-nanostructure interactions and the development of microrheology has attracted many interests in developing theoretical compressible models for the viscoelastic fluids \cite{yu2015compressible,galstyan2015note,chakraborty2015constitutive,pelton2009damping,squires2009fluid}. The compressibility of the fluids has a significant effects on the breathing modes of nanoparticles immersed in viscoelastic fluids like water-glycerol mixtures. In microrheology, the understanding of the compressibility effect of the elastic components on the flowing behavior is important \cite{yu2015compressible,galstyan2015note,chakraborty2015constitutive,pelton2009damping}. The compressibility effect is also vital in the other applications like understanding bubble dynamics \cite{lind2013bubble} and modeling injecting/compression process in plastic engineering \cite{kim1999numerical}. It is a challenge to develop reasonable mathematical models to explain the experimental results and to help understanding more complex phenomena.
%%Many theoretical models have been developed over the past years. In most macroscopic models, the hydrodynamic properties are described by the compressible classical Navier-Stokes equations or Euler equations with the stress determined by a constitutive equation, which is a relationship between the stress and velocity fields or strain measures and is responsible for the rheological properties \cite{larson1999structure}.
% %Most of the compressible models developed in the literatures
% are obtained by modifying the classical incompressible Oldroyd-B or Upper-Convected-Maxwell (UCM) model \cite{beris2013thermodynamics,ottinger2005beyond,edwards1990remarks,belblidia2006stabilised,bollada2012mathematical,chakraborty2015constitutive}. These models consist of Oldroyd-B derivatives or other objective derivates, which are widely used to meet the principle of material indifference to guarantee the coordinate independence of the models. However, to generalize the incompressible models to the compressible case is not trial. Actually, according to \cite{bollada2012mathematical}, a widely accepted compressible model is not available. In \cite{bollada2012mathematical}, the models proposed in \cite{edwards1990remarks,beris2013thermodynamics,wilmanski2008continuum,belblidia2006stabilised} are discussed and a isothermal UCM like constitutive equations are derived.
%
% %Among these models, \cite{edwards1990remarks} adds an additional term with divergence of velocity multiplying by the stress in the UCM model, \cite{wilmanski2008continuum} adds a term with the contraction of stress tensor and velocity gradient tensor, and \cite{belblidia2006stabilised} decompose the stress into non-Newtonian polymeric parts and Newtonian solvent parts. In the model derived in \cite{bollada2012mathematical}, the dependence of viscosity on density is considered.
%
% In \cite{chakraborty2015constitutive}, the compressible constitutive equations \cite{edwards1990remarks,sureshkumar2004stability,yong2014newtonian} are studied in the linear case with the Newtonian limit and high-frequency limit. Most of the models \cite{edwards1990remarks,sureshkumar2004stability} except the model proposed in \cite{yong2014newtonian} do not capture the proper response in the high-frequency limit. The compressional relaxation spectrum is considered in \cite{yong2014newtonian} while the others, mostly obtained by modifying the UCM or Oldroyd-B models, ignore it. However, the model in \cite{yong2014newtonian} is linear and violates the material indifference principle. In \cite{qian2010global,hu2011global}, a compressible models is proposed by generalizing the model \cite{lin2005hydrodynamics} using deformation tensor evolution equations in nonlinear continuum mechanics.
%
%Unlike the thermodynamics considerations is largely avoided with the assumption of incompressibility in the modeling of viscoelastic fluids, it is important in developing compressible viscoelastic fluid models. Most of the models derived from modifying the classical models \cite{edwards1990remarks,wilmanski2008continuum,belblidia2006stabilised,sureshkumar2004stability} or from the mathematical considerations \cite{qian2010global,hu2011global,yong2014newtonian}, do not take the temperature into consideration and their consistency with thermodynamic laws are not clear. It is expected that the constitutive equations should be derived from thermodynamic theories. Due to the non-conservative form of objective derivatives, the Posssion bracket formalism was not valid and a extended bracket formalism has been developed \cite{grmela1984bracket,morrison1984bracket,kaufman1984dissipative}. \"Ottinger and Grmela generalized it to develop the GENERIC formalism and applied the method in complex fluids \cite{grmela1997dynamicsI,ottinger1997dynamicsII,ottinger2005beyond}. It extends the Hamiltonian formalism for classical mechanics to general thermodynamic systems based on the second law of thermodynamics. Compared with the other models, a new configuration tensor is introduced with the stress as a function of it. The Oldroyd type derivatives are used in the evolution equations of the configuration tensor. And the second law of thermodynamics is satisfied with a explicit convex entropy formula. In a simple case without consideration of temperature, the model reads as
%\begin{subequations}\label{11}
%  \begin{align}
%  \partial_t \rho + \nabla \cdot (\rho \mathbf{v}) = 0, \\
%  \partial_t (\rho \mathbf{v}) + \nabla \cdot (\rho \mathbf{v}\mathbf{v} + p) + \nabla \cdot \pi =0, \\
%  \partial_t \mathbf{c} + \mathbf{v} \cdot \nabla \mathbf{c} + (\nabla \mathbf{v})  \mathbf{c }+ \mathbf{c}  (\nabla \mathbf{v})^T -(\nabla \mathbf{v} +(\nabla \mathbf{v})^T ) = -\frac{\mathbf{c}}{\tau}. \label{113}
%\end{align}
%\end{subequations}
%Here $\pi=2\mathbf{c} \cdot (\mathbf{c}-\mathbf{I})-\frac{1}{2}tr(\mathbf{c}^2)\mathbf{I}$, $\mathbf{I}$ is the identity tensor and $tr(\mathbf{c}^2) = \sum_{i,j}c_{ij}c_{ji}$, $\nabla \mathbf{v}=[ \partial_{x_j} v_i]$. And $\tau$ is a relaxation time related to the viscosity of the fluid. $\mathbf{c}$ is called configuration tensor. At equilibrium $\mathbf{c} =0$. $p$ is the pressure which depends only on the density. Notice that the first two equations are the same with Navier-Stokes equations and Euler equations in hydrodynamics. The third equation is the constitutive equation for the configuration tensor. The stress $\pi$ is a function of the configuration tensor $\mathbf{c}$.
%
%In recent years, there has been a substantial interests in the mathematical analysis of compressible viscoelatic fluids \cite{lei2006global,fang2014incompressible,hu2011global,qian2010global,hu2013global,hu2010local,qian2011initial}. The non-conservative Oldroyd type derivatives and the inclusion of density equations are the main difficulty. Most work is concerned with the local existence and global existence near equilibrium of smooth solutions. In the whole space, the local and global existence near equilibrium of smooth solutions to the generalized compressible model of the incompressible case \cite{lin2005hydrodynamics} are proved in the Besov spaces. The initial-boundary problem is investigated in \cite{qian2011initial}. The local and global existence of smooth solutions to a weakly compressible Oldroyd-B model is proved in \cite{guillope2010regular}. The incompressible limit in the whole space is discussed in \cite{lei2006global}. And the incompressible limit of Oldroyd-B fluids is studied in \cite{fang2014incompressible}. Most of these work rewrites the equations in a hyperbolic-parabolic system and deal with the non-conservative terms treated separately. In \cite{yong2014newtonian}, Yong proposed a linear Maxwell like model and studied its compatibility with Navier-Stokes equations. It is based on the fact the the system is a conservative balance system with entropy.
%
%The main goal of this paper is to establish the global existence of smooth solutions for the system \label{11} in one-dimensional case and justify the compatibility with Navier-Stokes equations. The one-dimensional version is
%\begin{subequations}\label{12}
%  \begin{align}
%  \partial_t \rho + \partial_x (\rho v) = 0 , \\
%\partial_t (\rho v) + \partial_x (\rho v^2) + \partial_x p + (3c-2) \partial_x c = 0, \\
%\partial_t c + v \partial_x c + (2c-2) \partial_x v =-\frac{c}{\tau}.
%\end{align}
%\end{subequations}
%The global existence result is establishing with showing that this one-dimensional system is symmetrizable hyperbolic \cite{majda1984compressible} and dissipative in the sense of \cite{yong1992singular,yong1999singular} and satisfies the Kawashima condition \cite{kawashima1985systems}. With these good properties, the compatibility with the Navier-Stokes equations is also rigorously justified. The theorems we prove in this paper can not be generalized to the multi-dimensional case since in higher dimensions these good properties fail except the existence of entropy.
%
%
%
%%The constitutive equations describe the rheological properties of the fluids and are responsible for the elastic effects. They are usually a relation between the stress tensor and the strain measure. One of the most important principles for the constitutive equations to obey is the principle of material indifference \cite{oldroyd1950formulation}. This principle ensures that the property of the material is indifferent with the coordinate system. Following this principle, many incompressible models have been proposed. But in many situations the fluids may become compressible \cite{edwards1990remarks,bollada2012mathematical}. According to a recent survey \cite{bollada2012mathematical}, a widely accepted compressible model is not available yet.
%
%In recent years, compressible complex fluids attract more and more attention. the study on the interactions between viscoelastic
%fluids-nanostructure interactions and the development of microrheology has attracted many interests
%in developing theoretical compressible models for the viscoelastic
%fluids [1{5]. The compressibility of the
%fluids has a significant effects on the breathing modes
%of nanoparticles immersed in viscoelastic
%fluids like water-glycerol mixtures. In
%microrheology, the understanding of the compressibility effect of the elastic components
%on the
%flowing behavior is important [1{4]. The compressibility effect is
%also vital in other applications like understanding bubble dynamics [6] and
%modeling injecting/compression process in plastic engineering [7].
%%to study the fluid-structure interaction of nanoscale mechanical devices vibrating in simple liquids.
%to study the vibrations of nanoscale mechanical devices in simple liquids.
%bubble dynamics
%in plastic engineering
%
%Jaumann, (upper (lower) convected) Oldroyd
%
%"objective derivative".
%
%In \cite{}, the authors showed that a recently revised Maxwell model is the only correct one up-to-now in the linear regime.
%
%In \cite{ottinger2005beyond}, \"Ottinger proposed the following compressible model
%\begin{subequations}\label{11}
%  \begin{align}
%  \partial_t \rho + \nabla \cdot (\rho \mathbf{v}) = 0, \\
%  \partial_t (\rho \mathbf{v}) + \nabla \cdot (\rho \mathbf{v}\mathbf{v} + p) + \nabla \cdot \pi =0, \\
%  \partial_t \mathbf{c} + \mathbf{v} \cdot \nabla \mathbf{c} + (\nabla \mathbf{v})  \mathbf{c }+ \mathbf{c}  (\nabla \mathbf{v})^T -(\nabla \mathbf{v} +(\nabla \mathbf{v})^T ) = -\frac{\mathbf{c}}{\tau}. \label{113}
%\end{align}
%\end{subequations}
%Here $\pi=2\mathbf{c} \cdot (\mathbf{c}-\mathbf{I})-\frac{1}{2}tr(\mathbf{c}^2)\mathbf{I}$, $\mathbf{I}$ is the identity tensor and $tr(\mathbf{c}^2) = \sum_{i,j}c_{ij}c_{ji}$. $\nabla \mathbf{v}=[\partial_{x_j} v_i]$.
%And $\tau$ is a relaxation time related to the viscosity of the fluid.
%$\mathbf{c}$ is called configuration tensor. At equilibrium $\mathbf{c} =0$.
%proposed by \"Ottinger \cite{ottinger2005beyond} seems to be a promising model. It is based on a theory of irreversible thermodynamics and satisfies the laws of thermodynamics, which leads to an entropy structure of the model. In addition, the material indifference principle is satisfied with the Oldroyd type derivatives used in the equation of state.
%In this paper, we focus on the following model proposed in \cite{ottinger2005beyond}:
%
% In recent years, there has been a considerable interest in the mathematical analysis of viscoelastic fluids. For a survey see \cite{lin2012some,bollada2012mathematical}. For incompressible models, Lions and Masmoudi proved the global existence of weak solutions for a Maxwell model with Janumann derivatives \cite{lions1998incompressible}. It is based on an $L^2$ estimate on the constitutive equation. The nonconservative term due to the Janumann derivative cancels when taking contraction with the stress tensor. This result could not be extended to the Oldroyd case where the nonconservative terms can not be canceled. Lin and his collaborators studied a model without damping by observing the deformation tensor has divergence zero and rewrite the equations in the conservative form with a nonlinear term in the equation of momentum \cite{lin2005hydrodynamics}. For the compressible case, Yong proposed a Maxwell type model without convected derivatives and justified the Newtonian limit of the model \cite{yong2014newtonian}. The model is conservative and includes a damping source term. However, the model is not material indifference. The introduce of material indifference will make the equations of state not conservative. The method used in \cite{yong2014newtonian}  then could not be applied here.
%
%For viscoelastic fluid models with Oldroyd type derivatives, the main difficulty for mathematical analysis comes from the nonconservative terms. The model analyzed in this paper include the Oldroyd derivatives. The lack of basic energy estimate for the Oldroyd type model is overcome by expressing the stress tensor as a function of configuration tensor. The evolution equation for the configuration tensor is of Maxwell type similiar with the Lower Convected Mawell (LCM) model for complex fluids. The basic energy estimate could thus be obtained with the help of the entropy structure of the model. However, we want to prove the global existence of smooth solutions. And it requires a $H^s, s \ge 2$ estimate. Thanks to the symmetrizable property in the one dimensional case, the global existence results can be proved by a modification of the method in \cite{kawashima2009decay}. After rewritting the one dimensional equations into a symmetric dissipative hyperbolic system, we verify the Kawashima condition of the equations, leading to the global existence theorem.
%
%In developing constitutive equations for viscoelastic fluids, compatibility should always be taken into account. This means that, when the relaxation time is short, solutions to the viscoelastic model is close to the corresponding ones of the Navier-Stokes equations. The UCM model and Oldroyd-B model are both compatible with the Navier-Stokes equations formally. However a rigorous justification is difficult due to the nonconservative convected derivative. In \cite{yong2014newtonian}, the compatibility was justified rigorously by ignoring the nonlinear terms in the convected derivative. The model we considered here has convected derivatives. The first-order approximation using the Chapman-Enskog expansion ( or the Maxwell iteration) gives a Navier-Stokes system. It is formal in 3D. But in the one dimensional case, we could treat it rigorously. The validity of the expansion is shown by modifying the method developed in \cite{yang2015validity}.
%
%
%The first two equations are the continuity equation and momentum equations. The third one is the constitutive equation for the configuration tensor $\mathbf{c}$. It describes the rheological properties. Notice that in Ottinger's model the stress tensor $\pi$ is a function of the configuration tensor $\mathbf{c}$. The nonlinear terms $ \nabla \mathbf{v} \mathbf{c}$ and $\mathbf{c} (\nabla \mathbf{v})^T $ come from the material indifference of the Oldroyd-type derivative \cite{oldroyd1950formulation}, from which the materal indifference principle holds. The model differs from the Lower Convected Maxwell model in the expression of the stress tensor. It is widely known that an energy estimate of the Lower Convected Maxwell model is not available due to the Oldroyd type derivatives \cite{saut1990existence}. Due to its entropy structure, Ottinger's model has a natural energy estimate.
%
%In this paper, we will mostly deal with the one-dimensional version of \eqref{11}:
%\begin{subequations}\label{12}
%  \begin{align}
%  \partial_t \rho + \partial_x (\rho v) = 0 , \\
%\partial_t (\rho v) + \partial_x (\rho v^2) + \partial_x p + (3c-2) \partial_x c = 0, \\
%\partial_t c + v \partial_x c + (2c-2) \partial_x v =-\frac{c}{\tau}.
%\end{align}
%\end{subequations}
%We show that this one-dimensional system is symmetrizable hyperbolic \cite{majda1984compressible} and dissipative in the sense of \cite{yong1992singular,yong1999singular} and satisfies the Kawashima condition \cite{kawashima1985systems}. With these nice properties, we prove the global-in-time existence of classical solutions and justify the compatibility with the Navier-Stokes equations.
%
%The paper is organized as follows. In the next section an entropy function for model \eqref{11} is discussed. We then show that the one-dimensional system \eqref{12} is symmetrizable hyperbolic and dissipative and satisfies the Kawashima condition. The global existence result is established in Section 4. The last section is devoted to a proof of the compatibility with the Navier-Stokes equations.

\section{Convex Entropy}
\setcounter{equation}{0}

In this section, we discuss an entropy function for the non-conservative system \eqref{11} and show that the Hessian matrix of the entropy does not symmetrize the system. Write the configuration tensor $\mathbf{c}=[c_{ij}]$ as a column vector (see \eqref{25} below for the 2D case). Then the equations \eqref{11} and \eqref{12} can be rewritten as a system of partial differential equations
\begin{eqnarray}\label{21}
  U_t + \sum_{j=1}^d A_j(U) U_{x_j} = Q(U).
\end{eqnarray}
Here $U=U(x, t)$ is the unknown function from $\mathbf{R}^d \times [0,+\infty)$ to $\mathbf{R}^n$, each $A_j(U)$ is an $n\times n$-matrix-valued function and $Q(U)$ an $n$-vector-valued function for $U\in G$ (an open set to be determined below).



\subsection{Entropy}
Notice that the model \eqref{11} is not of conservative form. We firstly generalize the entropy definition for conservation laws \cite{friedrichs1971systems} to general first-order systems of form \eqref{21}.
%And then the entropy structure of \"Ottinger's model could be derived. Based on the entropy structure, an entropy estimate could be obtained for \"Ottinger's model.

\begin{defn}
A convex function $S=S(U)$ is called an entropy for the system \eqref{21}, if there exists a $d$-vector-valued function $J=J(U)$ such that all the smooth solutions of the system \eqref{21} satisfy
$$
S_t(U) = -\nabla \cdot J(U) + \sigma^S(U)
$$
with $\sigma^S(U) \le 0$.
\end{defn}

For model \eqref{11}, we can show the following function from \cite{ottinger2005beyond,yong2014newtonian}:
\begin{eqnarray}\label{22}
  S = S(\rho,\rho \mathbf{v} ,\mathbf{c}) = \phi(\rho) + \frac{(\rho \mathbf{v})^2}{2\rho} + \frac{1}{2} tr(\mathbf{c}^2),
  \end{eqnarray}
with $\phi(\rho) = \rho \int_{\rho_0}^\rho \frac{p(z)}{z^2} dz$, is an entropy. Indeed, it is easy to check that $S(U)$ is strictly convex in $U$ provided that $\phi_{\rho \rho} = p_{\rho} / \rho \ge 0$. The latter is physically reasonable for the pressure gets high as the density increases.

With formula \eqref{22} and the equations in \eqref{11} we can compute
\begin{eqnarray}\label{23}
  S_t &=& S_{\rho} \rho_t + S_{\rho \mathbf{v}} \cdot \mathbf{v}_t + S_\mathbf{c} : \mathbf{c}_t \nonumber\\
%  =-S_{\rho} {\rho}_t \nabla \cdot (\rho \mathbf{v}) - S_{\rho \mathbf{v}} \cdot ( \nabla \cdot (\rho \mathbf{v} \mathbf{v}) + \nabla p + \nabla \cdot \pi) - S_{\mathbf{c}} : (\mathbf{v} \cdot \nabla \mathbf{c} + (\nabla \mathbf{v})^T \cdot \mathbf{c} + \mathbf{c} \cdot \nabla \mathbf{v} - (\nabla \mathbf{v} +(\nabla \mathbf{v})^T)) -\frac{\mathbf{c}:\mathbf{c}}{\tau} \\
 % =-\nabla \cdot (S\mathbf{v}+p \mathbf{v}+ \mathbf{\pi} \cdot \mathbf{v}) + (\rho S_\rho + \rho \mathbf{v}^2-p-\phi(\rho)-\frac{1}{2}\rho \mathbf{v}^2) \nabla \cdot \mathbf{v} + (\mathbf{c}\cdot 2\mathbf{c}-2\mathbf{c}-\frac{1}{2} \mathbf{c}:\mathbf{c}\mathbf{I} - \mathbf{\pi}):\nabla \mathbf{v} - \frac{1}{\tau}\mathbf{c}:\mathbf{c} \\
  &=& -\nabla \cdot (S\mathbf{v}+p \mathbf{v}+ \mathbf{\pi} \cdot \mathbf{v}) - \frac{1}{\tau}\mathbf{c}:\mathbf{c} \\
  &\equiv& -\nabla \cdot J(U) + \sigma^S(U) .\nonumber
\end{eqnarray}
%with $\mathbf{J} = S \mathbf{v} + p\mathbf{v} + \pi \cdot \mathbf{v}$ and $\sigma^S = -\frac{\mathbf{c}:\mathbf{c}}{\tau}$.
This equation indicates that the change of local entropy is caused by the entropy flux $J(U)$ and the local entropy production rate $\sigma^S(U)$. The non-positiveness of $\sigma^S(U)$ guarantees the second law of thermodynamics.
Based on the equation above, we have the following identity
\begin{multline*}
\int_\Omega \left[\phi(\rho(x,t))+\frac{1}{2}\rho(x,t)|{\mathbf{v}}(x,t)|^2+\frac{1}{2} tr(\mathbf{c}(x,t)^2)\right] dx +\int_0^t \int_\Omega \frac{tr(\mathbf{c}(x,t)^2)}{\tau} dx dt \\
= \int_\Omega \left[\phi(\rho(x,0))+\frac{1}{2}\rho(x,0)|{\mathbf{v}}(x,0)|^2+\frac{1}{2} tr(\mathbf{c}(x,0)^2)\right] dx .
\end{multline*}

%\emph{Remark 1}. The basic energy estimate does not hold in the incompressible Lower Convected Maxwell model
%\begin{eqnarray*}
%  \partial_t \mathbf{v} + \mathbf{v} \cdot  \nabla \mathbf{v} + \nabla  p= \nabla \cdot \pi, \\
%  \partial_t \pi + \mathbf{v} \cdot \nabla \pi + (\nabla \mathbf{v})\pi + \pi(\nabla \mathbf{v})^T -(\nabla \mathbf{v} + (\nabla \mathbf{v})^T) = -\frac{\pi}{\tau}.
%\end{eqnarray*}
%Taking contraction with $\pi$ in both sides of the third equation, the additional term $2\mathbf{\pi}\cdot{\pi} : \nabla v$ could not be canceled with the second equation multipling $\mathbf{v}$. In the model \eqref{11}, the nonconservative term could be canceled due to the formula of $\pi$.
%
%\emph{Remark 2}. When $\tau$ is small, $\mathbf{c} \approx \tau (\nabla \mathbf{v}+(\nabla \mathbf{v})^T)$ and $\pi \approx -2\tau(\nabla \mathbf{v}+(\nabla \mathbf{v})^T)$, the approximate equations will be
%\begin{eqnarray*}
%  \partial_t \rho + \nabla \cdot (\rho \mathbf{v}) = 0, \\
%  \partial_t (\rho \mathbf{v}) + \nabla \cdot (\rho \mathbf{v}\mathbf{v} + p) = 4\tau \Delta \mathbf{v}.
%\end{eqnarray*}
%which is the Navier-Stokes system for the Newtonian fluid. So the model \eqref{11} is consistency with the Newtonian fluid model. We will treat it rigorously for the one dimensional case later in the paper.
%%Remark. $\pi$ have the same evolution of the maxwell model?


\subsection{Non-symmetrizable hyperbolicity}
For systems of conservation laws with a convex entropy, it is well-known that the Hessian matrix of the entropy symmetrizes the system in the sense of Friedrichs \cite{friedrichs1971systems}. Here we show that the Hessian matrix is not a symmetrizer for the nonconservative system \eqref{11} in the 1D and 2D cases.

For the one-dimensional case ($d=1$), we have
\begin{eqnarray}\label{24}
U=(\rho, \rho v, c)^T, \qquad Q(U) = \frac{1}{\tau}(0, 0, -c)^T, \nonumber\\
A(U) \equiv A_1(U) = \left( \begin{array}{ccc}
	0 & 1 & 0 \\[2mm]
	p_\rho-v^2 & 2v & 3c-2 \\[2mm]
	-\frac{(2c-2)v}{\rho} & \frac{2c-2}{\rho} & v
	\end{array} \right).
\end{eqnarray}
Compute
\begin{eqnarray*}
  S_{UU}(U) = & \frac{1}{\rho} \left( \begin{array}{ccc} p_{\rho} + v^2 & -v & 0\\[2mm]
    -v & 1 & 0 \\[2mm]
      0 & 0 & \rho \end{array} \right) , \\[4mm]
    S_{UU} A(U) = & \frac{1}{\rho} \left( \begin{array}{ccc} -(p_\rho-v^2)v & p_\rho-v^2 & -(3c-2)v \\[2mm]
      p_\rho-v^2 & v  & 3c-2 \\[2mm]
      -(2c-2)v & 2c-2 & \rho v \end{array} \right).
\end{eqnarray*}
Obviously, the product $S_{UU} A(U)$ is not symmetric.
But in this case, we can find a symmetrizer by modifying the Hessian matrix $S_{UU}(U)$ in the next section.


In the two-dimensional case, the model can be written as
\begin{eqnarray}\label{25}
  U_t + A_1(U) U_{x_1} + A_2(U) U_{x_2} =Q(U)
\end{eqnarray}
with $U = (\rho, v_1, v_2, c_1, c_2, c_3)^T$.
Notice that $\mathbf{c}=[c_{ij}]_{2\times 2}$ is assumed to be symmetric and we take $(c_1, c_2, c_3)= (c_{11}, c_{12}, c_{22})$. The coefficient matrices $A_1(U)$ and $A_2(U)$ have expressions
\begin{eqnarray*}
  A_1 (U) = \left( \begin{array}{cccccc} 0 & 1 & 0 & 0 & 0 & 0 \\[2mm]
    p_\rho-v_1^2 & 2 v_1 & 0 & 3c_1-2 & 2c_2 & -c_3 \\[2mm]
    -v_1 v_2 &  v_2 & v_1 & 2c_2 & 2(c_1 +c_3 -1) & 2c_2 \\[2mm]
    -\frac{2c_1-2}{\rho} v_1 & \frac{2c_1-2}{\rho} & 0 & v_1 & 0 & 0 \\[2mm]
    -\frac{c_2 v_1 +(c_1-1)v_2}{\rho} & \frac{c_2}{\rho} & \frac{c_1-1}{\rho} & 0 & v_1 & 0 \\[2mm]
    -\frac{2c_2 v_2}{\rho} & 0 & \frac{2c_2}{\rho} & 0 & 0 & v_1
  \end{array} \right), \\[4mm]
  A_2(U) = \left( \begin{array}{cccccc} 0 & 0 & 1 & 0 & 0 & 0 \\[2mm]
    -v_1 v_2 & v_2 & v_1 & 2c_2 & 2(c_1 +c_3-1) & 2c_2 \\[2mm]
    p_\rho-v_2^2 & 0 & 2v_2 & -c_1 & 2c_2 & 3c_3-2 \\[2mm]
    -\frac{2c_2 v_1}{\rho} & \frac{2 c_2}{\rho} & 0 & v_2 & 0 & 0 \\[2mm]
    -\frac{c_2 v_2 +(c_3-1)v_1}{\rho} & \frac{c_3-1}{\rho} & \frac{c_2}{\rho} & 0 & v_2 & 0 \\[2mm]
   -\frac{2c_3-2}{\rho} v_2 & 0 & \frac{2c_3-2}{\rho} & 0 & 0 & v_2 \end{array} \right).
\end{eqnarray*}

Compute
\begin{eqnarray*}
  S_{UU}(U) =\frac{1}{\rho} \left( \begin{array}{cccccc} p_\rho + v_1^2+v_2^2 & -v_1 & -v_2 &0 &0 &0 \\
    -v_1 & 1 & 0  & 0 & 0 & 0  \\
    -v_2 & 0 & 1 & 0 & 0 & 0  \\
    0 & 0 & 0 & \rho & 0 & 0 \\
    0 & 0 & 0 & 0 & 2\rho & 0 \\
    0 & 0 & 0 & 0 & 0 & \rho \end{array} \right).
\end{eqnarray*}
We see that the entry at the second row and sixth column of $S_{UU}(U)A_1(U)$ is $-c_3/\rho$, but that at the second column and sixth row is 0.
Meanwhile, the entry at the second row and sixth column of $S_{UU}(U) A_2(U)$ is $2c_2/\rho$, but that at the second column and sixth row is 0.
%{\small  \arraycolsep=1.4pt
%\begin{multline*}
%  S_{UU} A_1(U) =
%  \frac{1}{\rho} \cdot \\ \left( \begin{array}{cccccc} -(p_\rho -v_x^2-v_y^2)v_x & p_\rho-v_x^2 & -v_x v_y & (2-3c_1)v_x-2c_2 v_y & -2c_2 v_x -2(c_1+c_3-1)v_y & c_3 v_x-2c_2 v_y \\
%  p_\rho-v_x^2 & vx & 0 & 3c_1-2 & 2c_2 & -c_3 \\
%  -v_x v_y & 0 & v_x & 2c_2 & 2(c_1+c_3-1) & 2c_2 \\
%  (2-2c_1)v_x & 2c_1-2 & 0 & \rho v_x & 0 & 0 \\
%  -2c_2 v_x +(2-2c_1)v_y & 2c_2 & 2c_1-2 & 0 & 2\rho v_x & 0 \\
%  -2c_2 v_y & 0 & 2c_2 & 0 & 0 & \rho v_x
%  \end{array} \right),
%\end{multline*}
%and
%\begin{multline*}
%  S_{UU} A_2(U) =
%  \frac{1}{\rho} \cdot \\ \left( \begin{array}{cccccc} -(p_\rho-v_x^2-v_y^2)v_y & -v_x v_y & p_\rho-v_y^2 & -2c_2 v_x + c_1 v_y & 2(1-c_1-c_3)v_x-2c_2 v_y & -2c_2 v_x + (2-3c_3)v_y \\
%    -v_x v_y & v_y & 0 & 2c_2 & 2(c_1 + c_3 -1)  & 2c_2 \\
%    p_\rho-v_y^2 & 0 & v_y & -c_1 & 2c_2 & 3c_3-2 \\
%    -2 c_2 v_x & 2c_2 & 0 & \rho v_y & 0 & 0 \\
%    (2-2c_3)v_x - 2c_2 v_y & 2c_3-2 & 2c_2 & 0 & 2 \rho v_y & 0 \\
%    (2-2c_3)v_y & 0 & 2c_3-2 & 0 & 0 & \rho v_y \end{array} \right).
%\end{multline*}
%}
Therefore, the products $S_{UU}(U)A_1(U)$ and $S_{UU}(U)A_2(U)$ are not symmetric.

%Next we will show that the system \eqref{12} is symmetrizable hyperbolic in the sense of Friedrichs \cite{majda2012compressible}. To do this, we need to find a positive-definite  symmetric matrix $A_0(U)$ symmetrizing the coefficient matrix $A(U)$.
%In case \eqref{12} can be casted into a conservative form, the Hessian $S_{UU}$ of the convex entropy $S=S(U)$ is a natural symmetrizer. Now \eqref{12} can not be casted into a conservative form and the Hessian
%\begin{eqnarray}
%S_{UU} = \left( \begin{array}{ccc}
%  \frac{p_\rho}{\rho} + \frac{v^2}{\rho} & -\frac{v}{\rho} & 0 \\[2mm]
%  -\frac{v}{\rho} & \frac{1}{\rho} & 0 \\[2mm]
%	0 & 0 & 1  \end{array} \right)
%\end{eqnarray}
%does not symmetrize $A(U)$.

\section{Structural properties of the 1D model}
\setcounter{equation}{0}

In this section, we show that the one-dimensional system satisfies the second structural stability condition proposed in \cite{yong1992singular,yong2001basic} for general hyperbolic relaxation systems and the Kawashima condition \cite{kawashima1985systems}. We start with the structural stability condition.

\subsection{Structural stability}

For the one-dimensional model \eqref{12}, we define
\begin{eqnarray}\label{31}
A_0(U) = \frac{1}{\rho} \left( \begin{array}{ccc}
	 p_\rho  +v^2 & -v & 0 \\ [2mm]
	-v & 1 & 0 \\[2mm]
	0 & 0 & \frac{3c-2}{2c-2}\rho  \end{array} \right).
\end{eqnarray}
Obviously, both this $A_0(U)$ and the product
\begin{eqnarray*}
A_0(U) A(U) = \frac{1}{\rho} \left( \begin{array}{ccc}
		-(p_{\rho}-v^2)v & {p_\rho -v^2} & -{(3c-2)v} \\[2mm]
		{p_\rho-v^2} & {v} & {3c-2} \\[2mm]
		-{(3c-2)v} & {3c-2} & \frac{3c-2}{2c-2}\rho v
		\end{array} \right)
\end{eqnarray*}
are symmetric (see \eqref{24} for $A(U)$). Moreover, $A_0(U)$ is positive definite if
\begin{eqnarray*}
p_\rho > 0 \quad \mbox{and} \quad c < \frac{2}{3} \quad \mbox{or} \quad  c > 1 .
\end{eqnarray*}
For this reason, we take
\begin{equation}\label{37}
G := \{(\rho, v, c): \rho>0, \quad c< 2/3\}
% \ \mbox{or} \ > 1
\end{equation}
as the domain for the one-dimensional model.

%Since we only consider the global existence near equilibrium where $c=0$ in this paper, the smallness of $c$ guarantees the positive definite property of $A_0(U)$ near equilibrium.
%\subsection{Dissipativity}

Furthermore, with $A_0(U)$ constructed above it is clear that
\begin{equation}\label{32}
A_0(U_e)Q_U(U_e) + Q_U^T(U_e)A_0(U_e) =-\frac{2}{\tau}\mbox{diag}(0, 0, 1)
\end{equation}
for any equilibrium state $U_e = (\rho_e, 0, 0)^T$. Thus, the system \eqref{12} is dissipative in the sense of \cite{yong1992singular,yong1999singular}.

\subsection{Kawashima condition}

The model \eqref{12} is a nonconservative symmetrizable hyperbolic system with a convex entropy. For hyperbolic balance laws with a convex entropy, a general global existence result can be found in \cite{yong2004entropy,hanouzet2003global}. The proof was based on the Kawashima condition \cite{kawashima1985systems}.
%Actually, the Kawashima was proposed for the general symmetrizable hyperbolic system. It describes the dissipative property of the system. The condition is for the linear hyperbolic system.
Here we show that the system \eqref{12} satisfies the Kawashima condition by explicitly giving a compensating matrix $K$ \cite{kawashima1985systems}.

Set
\begin{eqnarray}\label{33}
K=\left( \begin{array}{ccc}
	0 & 1 & 0 \\
	-1 & 0 & -\rho_e \\
	0 & \rho_e & 0
	\end{array} \right)
\end{eqnarray}
(a skew-symmetric matrix) and $\bar{L} = \eta\mbox{diag}(0, 0, 1)$ (the diagonal matrix in \eqref{32}). Then we compute
\begin{eqnarray*}
K A(U_e) + (K A(U_e))^T + \bar{L} =
	\left( \begin{array}{ccc}
	2p_\rho(\rho_e) & 0 & \rho_e p_\rho(\rho_e) -2  \\
	0 & 2 & 0 \\
	\rho_e p_\rho(\rho_e) - 2 & 0 & \eta -4\rho_e 	
	\end{array} \right).
\end{eqnarray*}
This matrix is positive definite if
\begin{eqnarray*}
p_\rho > 0, \ \eta >4\rho, \ 2p_\rho(\eta - 4\rho)-(\rho p_{\rho}-2)^2 = 2 p_\rho\eta  - (2 + \rho p_\rho)^2 >0.
\end{eqnarray*}
The first inequality is a physical requirement for $p=p(\rho)$. The last two inequalities are true provided that
$$
\eta \geq 2\rho_e +\frac{(2 + \rho_e p_\rho(\rho_e))^2}{2 p_\rho(\rho_e)}.
$$
Thus, for sufficiently large $\eta$, we have
\begin{eqnarray}\label{35}
K A(U_e) + (K A(U_e))^T + \bar{L} \ge C_s I
\end{eqnarray}
with $I$ the $3 \times 3$ unit matrix and $C_s$ a positive constant depending only on $\rho_e$.

\section{Global existence}
\setcounter{equation}{0}

In this section, we prove that the one-dimensional model \eqref{12} allows global smooth solutions near equilibrium states, although it contains non-conservative equations. Here we fix the relaxation time $\tau=1$. The proof is similar to that in \cite{yong2004entropy,kawashima2009decay} for hyperbolic balance laws, but we have to deal with the non-conservative equations. We use the standard notation from \cite{yong2004entropy,kawashima2009decay} and the main result reads as
%The main difficulty here is the lack of conservation laws, which is crucial in deriving $L^2$ estimate of $U$ in \cite{yong2004entropy}. Here we also use the entropy to derive $L^2$ estimate following the concrete analysis of the equation. The high order derivative estimate follows the reference \cite{yong2004entropy}. The Kawashima condition is used to obtain the $L^2_t(H^s_X)$ estimate of $U$ which is important to obtain the global existence result \cite{yong2004entropy}.

\begin{thm} \label{theoremglobal}
  Let $s \ge 2$ be an integer. Assume $U_0=U_0(x) \in H^s(\mathbb{R})$ and $\|U_0 -U_e\|_{H^s}$ is sufficiently small. Then there is a unique global solution $U=U(x,t)$ to the system \eqref{12} with initial data $U_0$ satisfying
$$
U-U_e \in C([0,+\infty),H^s(\mathbb{R}))
$$
and
\begin{eqnarray}\label{41}
\|U(T)-U_e\|^2_{H^s} + \int_0^T \left[ \|c(t)\|^2_{H^s} + \|\partial_x U(t)\|^2_{H^{s-1}} \right] dt \le C \|U_0 -U_e\|^2_{H^s}
\end{eqnarray}
for all $T>0$, where $C$ is a positive constant independent of $T$.
\end{thm}

\begin{proof}
Since the system  \eqref{12} is symmetrizable hyperbolic, by the standard theory
%the system \eqref{12}, defined in the open convex set $G$
\cite{majda1984compressible, kato1975cauchy} it has a unique local-in-time $H^s$ solution with initial data $U_0$. Then the global existence follows from a standard continuation argument (see, e.g., \cite{yong2004entropy}) based on the {\it a priori} estimate \eqref{41}. Thus, it is sufficient to get the {\it a priori} estimate, which will be done with the following three steps.

%The proof is divided into three steps. We first derive the basic $L^2$ estimate. And then the higher order derivative estimate is obtained by differentiate the system. Then the Kawashima condition is utilized to get the $L_t(H^s)$ estimate for $U$. The global existence result then follows from these estimates.

\emph{Step 1.} Define
\begin{eqnarray*}
E=E(U,U_e) = S(U)-S(U_e)-S_U(U_e)(U-U_e).
\end{eqnarray*}
Since $S=S(U)$ is strictly convex, there exist two positive constants $c_1$ and $C_1$ such that
\begin{eqnarray}\label{42}
c_1 |U-U_e|^2 \le E(U,U_e) \le C_1 |U-U|^2
\end{eqnarray}
for all $U$ close to $U_e$. On the other hand, from \eqref{23} and \eqref{21} we compute
\begin{eqnarray}\label{43}
E_t = S_t - S_U(U_e)U_t = -\nabla \cdot J(U) - \frac{c^2}{\tau} - S_U(U_e)(Q(U) - A(U)U_x).
\end{eqnarray}
Notice that
\begin{eqnarray*}
S_U(U_e) A(U) U_x &=& (\phi_\rho(\rho_e), 0, 0)
\left( \begin{array}{ccc}
0 & 1 & 0 \\
p_\rho-v^2 & 2v & 3c-2 \\
-\frac{2c-2}{\rho} & -\frac{2c-2}{\rho} & v
\end{array} \right)
\left( \begin{array}{ccc}
\rho \\ \rho v \\ c \end{array} \right)_x \\
&=& \phi_\rho(\rho_e) (\rho v )_x,
\end{eqnarray*}
we integrate the equation \eqref{43} over $(x, t)\in(-\infty, + \infty)\times[0,T]$ to obtain
\begin{eqnarray*}
\int_\mathbb{R}E(U(x, T), U_e)dx - \int_\mathbb{R} E(U_0, U_e)dx = - \int_0^T\int_\mathbb{R} \frac{c^2(x, t)}{\tau} dx dt.
\end{eqnarray*}
Combining this with \eqref{42}, we arrive at the following basic $L^2$ estimate
\begin{eqnarray}\label{44}
\|U(\cdot, T)-U_0\|^2_{L^2} + \int_0^T \|c(\cdot, t)\|^2_{L^2}dt \le C\|U_0 - U_e\|^2_{L^2},
\end{eqnarray}
where $C$ is a generic constant.

\emph{Step 2.} Next we estimate the higher-order derivatives. Let $l\le s$ be a positive integer. We take the $l$-th order derivative with $x$ in both sides of the system \eqref{21} to obtain
\begin{eqnarray*}
\partial^l_x U_t + A(U) \partial^l_x U_x = \partial^l_x Q(U) + [A(U),\partial^l_x]U_x.
\end{eqnarray*}
where $[X,Y]=XY-YX$ is the commutator. Since $A_0(U)$ and $A_0(U)A(U)$ are symmetric, we take the $L^2$-inner product with $A_0(U)\partial^l_x U$ to get
\begin{multline}\label{45}
  (A_0(U)\partial^l_x U,\partial^l_x U)_t + \int (\partial^l_x U^T A_0(U)A(U)\partial^l_x U)_x dx \\
  = ((\partial_t A_0(U)+\partial_x(A_0(U)A(U)))\partial^l_x U,\partial^l_x U) \\
  + 2(A_0(U)[A(U),\partial^l_x]U_x,\partial^l_x U) + 2(A_0(U) \partial^l_x Q(U), \partial^l_x U).
\end{multline}
Since $U(\cdot, t)\in H^s(\mathbb{R})$ for each $t$, the second term on the left-hand side vanishes.
%It follows from the postive definite property of $A_0(U)$ that
%\begin{eqnarray}
%  (A_0(U)\partial^l_x U, \partial^l_x U) \ge C \|\partial^l_x U\|^2_{L^2}
%\end{eqnarray}
The three terms on the right-hand side can be estimated as follows.

For the first term we have
\begin{eqnarray}\label{HsEST:1}
  && ((\partial_t A_0(U) + \partial_x (A_0(U)A(U)))\partial^l_x U, \partial^l_x U) \nonumber\\
  &\le&|\partial_t A_0(U) + \partial_x (A_0(U)A(U))|_{L^\infty}\|\partial^l_x U\|_{L^2}^2 \nonumber\\
  &\le& C (|\partial_t U|_{L^\infty}+|\partial_x U|_{L^{\infty}})\|\partial^l_x U\|_{L^2}^2  \\
  &\le& C (|\partial_x U|_{L^\infty}+|Q(U)|_{L^\infty})\|\partial^l_x U\|_{L^2}^2\nonumber\\
  &\le& C (|\partial_x U|_{L^\infty} + |c|_{L^\infty}) \|\partial^l_x U\|_{L^2}^2\nonumber \\
  &\le& C \|U-U_e\|_{H^s} \|\partial^l_x U\|_{L^2}^2. \nonumber
\end{eqnarray}
The second term can be estimated as
\begin{eqnarray*}
  2(A_0(U) [A,\partial^l_x] U_x, \partial^l_x U) \le C |A_0(U)|_{L^\infty} \|[A(U),\partial^l_x] U_x\|_{L^2} \|\partial^l_x U\|_{L^2}.
\end{eqnarray*}
For the commutator we use the calculus inequalities in Sobolev spaces \cite{majda1984compressible} to obtain
\begin{eqnarray*}
  \|[A(U),\partial^l_x] U_x\|_{L^2} &\le& C (\|\partial_x^s A(U)\|_{L^2}|U_x|_{L^\infty} + |\partial_x A(U)|_{L^{\infty}} \|\partial_x^{s-1} U_x\|_{L^2})  \\
  &\le& C|U_x|_{L^\infty} \|\partial_x^s U\|_{L^2}.
\end{eqnarray*}
Thus, we have
\begin{eqnarray}\label{HsEST:2}
  2(A_0(U) [A,\partial_x^l] U_x,\partial^l_x U) \le C \|U-U_e\|_{H^s}\|\partial_x U\|_{H^{s-1}}^2.
\end{eqnarray}
For the third term we recall the expressions of $Q(U)$ and $A_0(U)$ in \eqref{24} and \eqref{31} to get
\begin{eqnarray}\label{HsEST:3}
&& 2(A_0(U)\partial^l_x Q(U),\partial^l_x U) \nonumber \\
&=& 2( A_0(U_e)\partial^l_x Q(U),\partial^l_x U) + 2((A_0(U)-A_0(U_e)) \partial^l_x Q(U),\partial^l_x U) \nonumber \\
&\le&  -2 \|\partial^l_x c\|_{L^2}^2 + C|U-U_e|_{L^\infty} \|\partial^l_x U\|_{L^2}^2 \nonumber \\
&\le& -2 \|\partial^l_x c\|_{L^2}^2 + C\|U-U_e\|_{H^s} \|\partial^l_x U\|_{L^2}^2
\end{eqnarray}

Having the inequalities \eqref{HsEST:1},\eqref{HsEST:2} and \eqref{HsEST:3}, we integrate \eqref{45} over $[0,T]$ to obtain
\begin{eqnarray}\label{49}
  \|\partial^l_x U(T)\|_{L^2}^2&  + & \int_0^T \|\partial^l_x c(t)\|^2_{L^2}dt \le C\|\partial^l_x U(0)\|_{L^2}^2  \nonumber\\[3mm]
 & +& C\sup_{t \in [0,T]}\|U(t)-U_e\|_{H^s} \int_0^T \|\partial_x U(t)\|^2_{H^{s-1}}dt .
\end{eqnarray}
Here we have used the following fact that
\begin{eqnarray*}
   C^{-1} \|\partial^l_x U\|_{L^2}^2 \le  (A_0(U) \partial^l_x U,\partial^l_x U) \le C \|\partial^l_x U\|_{L^2}^2.
\end{eqnarray*}
Adding \eqref{44} and \eqref{49} with $1 \le l \le s$, we arrive at the following estimate
  \begin{eqnarray}\label{210}
    && \|U(T)-U_e\|^2_{H^{s}}  +  \int_0^T \|c(t)\|^2_{H^s} dt \nonumber \\
    & \le & C \|U_0-U_e\|_{H^{s}}^2 + C \sup_{t \in [0,T]} \|U(t) - U_e\|_{H^s} \int_0^T \|\partial_x U\|_{H^{s-1}}^2dt.
%  \\  \le C \|\partial_x U_0\|^2_{H^{s-1}} + C M(t)D_0(t)^2
\end{eqnarray}

\emph{Step 3.} Next we use the Kawashima condition to control the second term in the last inequality. For this purpose,  we rewrite \eqref{21} as
\begin{eqnarray*}
  U_t + A(U_e) U_x  = (A(U_e) -A(U))U_x + Q(U).
\end{eqnarray*}
From this equation, we take the $l$-th derivative with $x$ and multiply by the compensating matrix $K$ to obtain
\begin{eqnarray*}
  K \partial^l_x U_t + K A(U_e) \partial^l_x U_x  = K \partial^l_x ((A(U_e)-A(U))U_x) + K\partial^l_x Q(U).
\end{eqnarray*}
Then taking the inner product with $\partial^l_x U_x$ we get
\begin{eqnarray}\label{211}
  (K \partial^l_x U_t, \partial^l_x U_x) + (KA(U_e) \partial^l_x U_x, \partial^l_x U_x) \nonumber \\ = (K \partial^l_x((A(U_e)-A(U))U_x),\partial^l_x U_x) + (\partial^l_x( K Q(U) ),\partial^l_x U_x).
\end{eqnarray}
Recall that the matrix $K$ is skew-symmetric. The first term on the left-hand side of the last equation can be treated as
\begin{eqnarray}\label{212}
  (K\partial^l_x U_t, \partial^l_x U_x) &=& \frac{1}{2} \int_\mathbb{R} \left[(\partial^l_x U^T_x K \partial^l_x U )_t -  (\partial^l_x U_t^T K\partial^l_x U  )_x \right]dx  \nonumber \\
  &=& \frac{1}{2}(K \partial^l_x U,\partial^l_x U_x)_t .
\end{eqnarray}
For the second term, we use \eqref{35} to get
\begin{eqnarray}\label{213}
  2(KA(U_e) \partial^l_x U_x,\partial^l_x U_x) &=& ( (KA(U_e)+ (K A(U_e))^T +\bar{L}) \partial^l_x U_x, \partial^l_x U_x) - (\bar{L}\partial^l_x U_x, \partial^l_x U_x) \nonumber\\
  &\ge& C_s \|\partial^l_x U_x \|^2_{L^2} -\eta \|\partial^l_x c\|^2_{L^2},
\end{eqnarray}

The right-hand side of \eqref{211} can be simply estimated as
\begin{eqnarray}\label{214}
  (K \partial^l_x Q(U),\partial^l_x U_x) \le \epsilon \|\partial^l_x U_x\|_{L^2}^2 + \frac{C}{\epsilon} \|\partial^l_x c\|_{L^2}^2
\end{eqnarray}
and
\begin{eqnarray}\label{215}
  && (K\partial^l_x ((A(U_e)-A(U))U_x),\partial^l_x U_x) \le \epsilon\|\partial^l_x U_x\|_{L^2}^2 + \frac{C}{\epsilon} \|\partial^l_x( (A(U_e)-A(U))U_x)\|_{L^2}^2 \nonumber \\
  &\le& \epsilon \|\partial^l_x U_x \|_{L^2}^2 + C(\epsilon)( |A(U_e)-A(U )|_{L^\infty}^2 \|\partial^l_x U_x\|^2_{L^2}+\|\partial^l_x A(U)\|_{L^2}^2|U_x|_{L^\infty}^2) \nonumber \\
  &\le& \epsilon \|\partial^l_x U_x\|_{L^2}^2 + C(\epsilon) (|U-U_e|_{L^\infty}^2 \|\partial^l_x U_x\|_{L^2}^2 + |U_x|_{L^\infty}^2 \|\partial^l_x U\|_{L^2}^2).
\end{eqnarray}
Here we have used the calculus inequalities in Sobolev spaces.

Using the above inequalities \eqref{212}--\eqref{215}, we deduce from \eqref{211} that
\begin{multline*}
  C_s \|\partial^l_x U_x\|^2_{L^2} \le (\eta+\frac{C}{\epsilon}) \|\partial^l_x c\|_{L^2}^2-\frac{1}{2} (K \partial^l_x U,\partial^l_x U_x)_t  + 2\epsilon \|\partial^l_x U_x\|^2_{L^2} \\
  +C(\epsilon) |U-U_e|_{L^\infty}^2 \|\partial^l_x U_x\|_{L^2}^2 + C(\epsilon) |U_x|_{L^\infty}^2 \|\partial^l_x U\|_{L^2}^2.
\end{multline*}
Choose $\epsilon$ sufficiently small (for example $\epsilon = C_s/4$). By integrating the last inequality over $[0,T]$, we arrive at
\begin{multline*}
  \int_0^T \|\partial^l_x U_x(t)\|^2_{L^2} dt \le C \int_0^T \|\partial^l_x c(t)\|^2_{L^2} dt
  +C\|\partial^l_x U(T)\|_{H^1}^2 + C\|\partial^l_x U_0\|_{H^1}^2 \\
  + C \sup_{t\in [0,T]} (|U(t)-U_e|_{L^\infty}^2 + |U_x(t)|_{L^\infty}^2) \int_0^T \|\partial^l_x U(t)\|_{L^2}^2 dt
\end{multline*}
for $1\le l \le s-1$. Adding this inequality from $1 \le l \le s-1$ gives
\begin{multline}\label{216}
  \int_0^T \|\partial_x U(t)\|^2_{H^{s-1}} dt \le C \int_0^T \|c(t)\|^2_{H^s} dt + C\|U_0-U_e\|^2_{H^s} + C\|U(T)-U_e\|^2_{H^s} \\+C \sup_{0 \le t \le T}(|U(t)-U_e|_{L^\infty}^2 + |U_x(t)|_{L^\infty}^2) \int_0^T \|\partial_x U(t)\|_{H^{s-1}}^2 dt \\
  \le C \int_0^T \|c(t)\|_{H^s}^2 dt + C \|U_0-U_e\|_{H^s}^2 + C\|U(T) -U_e\|_{H^s}^2  \\ + C \sup_{t \in [0,T] }\|U(t)-U_e\|_{H^s}^2 \int_0^T \|\partial_x U(t)\|_{H^{s-1}}^2 dt.
\end{multline}

Let $\alpha$ be a positive number. We multiply \eqref{216} with $\alpha$ and then add the resultant inequality to \eqref{210} to get
\begin{eqnarray*}
  \|U(T)-U_e\|_{H^s}^2 + \int_0^T \|c(t)\|_{H^s}^2 dt + \alpha \int_0^T \|\partial_x U(t)\|_{H^{s-1}}^2 dt \\
  \le C \alpha \int_0^T \|c(t)\|_{H^s}^2 dt +C(1+\alpha)\|U_0 -U_e\|_{H^s}^2 + C \alpha \|U(T)-U_e\|_{H^s}^2  \\ + C(\sup_{t \in [0,T]} \|U(t)-U_e\|_{H^s} + \alpha \sup_{t \in [0,T]} \|U(t)-U_e\|_{H^s}^2)  \int_0^T \|\partial_x U\|_{H^{s-1}}^2 dt.
\end{eqnarray*}
With $\alpha$ sufficiently small, the last inequality leads to
\begin{eqnarray*}
  \|U(T)-U_e\|_{H^s}^2 + \int_0^T \|c(t)\|_{H^s}^2 dt + \int_0^T \|\partial_x U(t)\|_{H^{s-1}}^2 dt \\
  \le C \|U_0-U_e\|_{H^s}^2 + C \sup_{t \in [0,T]} \|U(t)-U_e\|_{H^s} \int_0^T \|\partial_x U(t)\|_{H^{s-1}}^2 dt \\
  +C\alpha  \sup_{t \in [0,T]} \|U(t)-U_e\|_{H^s}^2 \int_0^T \|\partial_x U(t)\|_{H^{s-1}}^2 dt.
\end{eqnarray*}
From this the {\it a prior} estimate in Theorem 4.1 follows if $\|U_0 -U_e\|_{H^s} $ is sufficiently small. This completes the proof.

\end{proof}
\section{Compatibility
%with the Navier-Stokes equations
}
\setcounter{equation}{0}

In this section, we show that the 1D model \eqref{12} is compatible with the Navier-Stokes equations as the relaxation time $\tau$ tends to zero. Formally, this can be simply seen with the Maxwell iteration. Indeed, we rewrite the third equation in \eqref{12} as
\begin{eqnarray*}
  c= -\tau(\partial_t c + v \partial_x c + (2c-2) \partial_x v)
\end{eqnarray*}
and iterate this relation once to obtain
\begin{eqnarray*}
  c = 2 \tau \partial_x v + O(\tau^2).
\end{eqnarray*}
Substituting the truncation into the second equation in \eqref{12},
we arrive at the 1D isentropic Navier-Stokes equations
  \begin{align}\label{51}
  \partial_t \rho + \partial_x (\rho v ) = 0, \nonumber \\
  \partial_t (\rho v) + \partial_x( \rho v^2 + p) = 4 \tau \partial^2_x v
\end{align}
with $4\tau$ as the viscosity coefficient. The rest of this section is to justify the above formal derivation of \eqref{51} from \eqref{12}.

Our justification is similar to that in \cite{yang2015validity} but we have to deal with the non-conservative terms in \eqref{12}. The main result reads as

\begin{thm}\label{theoremCE}
Let $s \ge 2$ be an integer and ${\bar u} =({\bar \rho}(x),\bar{\rho}(x){\bar v}(x))$ satisfy
  \begin{eqnarray*}
    \bar{u}\in H^{s+2} \quad  \mbox{and} \quad \inf_{x} \bar{\rho}(x)>0.
 \end{eqnarray*}
Then there exists $T_*>0$, independent of $\tau$, such that the 1D system \eqref{12} with initial data $(\bar{u},0)$ and the Navier-Stokes system \eqref{51} with initial data ${\bar u}$ have unique solutions $(u^\tau=(\rho^\tau,\rho^\tau v^\tau), c^\tau)(x,t)$ and $u^\tau_p=(\rho^\tau_p,\rho^\tau_p v^\tau_p)(x,t)$ in $C([0,T_*], H^s)$ satisfying
  \begin{equation}\label{52}
    \sup_{t \in [0, T_*]} \|(u^\tau-u^\tau_p)(\cdot,t)\|_{H^s} \le C(T_*) \tau^2
  \end{equation}
  for $\tau$ sufficiently small. Here $C(T_*)>0$ is independent of $\tau$.
\end{thm}

\begin{rem}
For the sake of simplicity, Theorem 2 is stated only for the special initial data. But it holds with \eqref{52} replaced by
\begin{equation*}\label{eq:Result}
    \sup_{t \in [-\tau\ln\tau, T_*]} \|(u^\tau-
    %u'_\tau-
    u^\tau_p)(\cdot,t)\|_{H^s} \le C(T_*) \tau^2,
  \end{equation*}
due to initial layers, for more general initial data
${\tilde u}_p =({\tilde \rho}_p(x, \tau),\tilde{\rho}_p(x,\tau){\tilde v}_p(x, \tau))$ for \eqref{51} and $ ({\tilde u} =({\tilde \rho}(x, \tau),\tilde{\rho}(x,\tau){\tilde v}(x, \tau)), \tilde {c}(x, \tau))$ for \eqref{12} satisfying
  \begin{eqnarray*}
    \tilde{u}_p(\cdot,\tau),\tilde{u}(\cdot,\tau),\tilde{c}(\cdot,\tau) \in H^{s+2}, \quad  \inf_{x, \tau} \tilde{\rho}_p(x,\tau), \inf_{x, \tau} \tilde{\rho}(x,\tau)>0, \quad \sup_{x, \tau} \tilde{c}(x,\tau)< 2/3, \nonumber  \\
    \|\tilde{\rho}(\cdot,\tau)-\tilde{\rho}_p(\cdot,\tau)\|_{H^s}, \| \tilde{\rho} \tilde{v}(\cdot,\tau)-\tilde{\rho}_p\tilde{v}_p(\cdot,\tau)- \frac{3}{2} \tau \bar{c}_{0x} \bar{c}_0 +2 \tau \bar{c}_{0x}\|_{H^s}  = O(\tau^2)
  \end{eqnarray*}
  with $\bar{c}_0=\tilde{c}(x,0)$. This general statement can be proved by slightly modifying the proof below.
\end{rem}

To prove the above theorem, we first  recall that the 1D system \eqref{12} satisfies the second structural stability condition \cite{yong1992singular,yong1999singular}. Therefore, the singular perturbation theory developed therein applies. Namely, the solution $U^\tau = (\rho^\tau, \rho^\tau v^\tau, c^\tau)^T$ to \eqref{12} with initial data $(\bar{u},0)$ exists in the time interval $[0,T_*]$ where an approximate solution $U_\tau^1=(\rho_\tau^1,\rho_\tau^1 v_\tau^1, c^1_\tau)^T$
was constructed and satisfies
\begin{eqnarray}\label{53}
  \sup_{t \in [0, T_*]} \|U^\tau(\cdot, t) - U_\tau^1(\cdot, t)\|_{H^s} \le K\tau^2
\end{eqnarray}
with $K$ a positive constant independent of $\tau$. Thus, the existence of $U^\tau$ on the time interval $[0,T_*]$ is out of question.

To show the other conclusions of the theorem, we refer to \cite{yong1992singular,yong1999singular} for the construction of the approximate solution $U_\tau^1$, which has the form
\begin{eqnarray*}
U^1_\tau  = U_0(x,t) + \tau U_1(x,t) + U'_0(x,t') + \tau U'_1(x,t')
\end{eqnarray*}
with $t'=t/\tau$.
Here the coefficients $U_0=(u_0, c_0)$ and $U_1=(u_1, c_1)$ of the outer solution solve
\begin{eqnarray}
  c_0 = 0, \quad
  \partial_t u_0+ \partial_x f(u_0,0)=0 , \nonumber \\
  c_1 = 2\partial_x v_0, \quad
  \partial_t u_1 + \partial_x (f_u(u_0,0) u_1)  -4 \partial^2_x v_0 = 0 \label{54}
\end{eqnarray}
with
\begin{eqnarray*}
  f(\rho,\rho v,c) = \left( \begin{array}{cc} \rho v \\ \rho v^2 + p + \frac{3}{2} c^2 - 2c \end{array} \right);
\end{eqnarray*}
while $U_0'=(u_0', c_0')$ and $U_1'=(u_1', c_1')$ satisfy
\begin{eqnarray*}
 \partial_{t'} u'_0 = 0,  \quad \partial_{t'} c'_0 = -c'_0 , \\
  \partial_{t'} u'_1 = \partial_x(f(\bar u_0,0) - f(\bar u_0,c'_0)), \\
  \partial_{t'} c'_1 = - c'_1 - \bar v_0 \partial_x c_0' -2c_0'\partial_x \bar v_0.
\end{eqnarray*}
The required initial data for the above equations were obtained with the matching conditions
\begin{eqnarray*}
  \lim_{t' \to \infty} U'_0(x,t') = 0 , \quad \lim_{t' \to \infty} U'_1(x,t') = 0 .
\end{eqnarray*}
These and the requirement that the approximate solution should fulfil the prescribed initial condition lead to
\begin{eqnarray*}
 u'_0 =0, \quad u_0(x,0) = \bar{u}(x), \quad  c'_0 =c'_0(x,0)e^{-t/\tau}=0 , \\[4mm]
 u'_1(x,0) = -\partial_x\int_0^{+\infty} (f(\bar u_0,0) - f(\bar u_0,c'_0)) dt'=0\\
% = \partial_x\int_0^{+\infty} \left( \begin{array}{cc} 0 \\  \frac{3}{2} (c_0')^2 - 2c'_0 \end{array} \right) dt' =
 %\left( \begin{array}{cc} 0 \\  \frac{3}{2} \bar c_{0x}\bar c_0 - 2\bar c_{0x} \end{array} \right), \\[4mm]
 u_1(x,0) =  - u'_1(x,0)=0, \quad c'_1(x,0) = - 2\partial_x\bar v_0(x).
\end{eqnarray*}
These together with \eqref{53} show that
\begin{eqnarray*}
  \|u^\tau(\cdot, t) - u_0 (\cdot, t) - \tau u_1(\cdot, t) \|_{H^s} \le K \tau^2
\end{eqnarray*}
for $t \in [0,T_*]$. Thus, it reduces to establish

\addtocounter{thm}{-1}
\renewcommand{\thethm}{\arabic{thm}$'$}
\begin{thm}
  Under the conditions of Theorem 2, %hold and $\tilde{u}^1(\cdot,\tau) \in H^{s+2}$,$\tilde{u}_p(\cdot,\tau)\in H^s$ satisfy
the system \eqref{51} with initial data $\bar{u} $ has a unique solution $u_p^\tau \in C([0,T_*],H^s)$ satisfying
\begin{eqnarray}\label{eq:wcediff}
  \sup_{t \in [0,T_*]} \| u^\tau_p(\cdot,t) - u_0 (\cdot, t) - \tau u_1(\cdot, t)\|_{H^s} \le C \tau^2
\end{eqnarray}
for $\tau$ sufficiently small. Here $C=C(T_*)$ is independent of $\tau$.
\end{thm}

\begin{proof}
From the local existence theory of the Navier-Stokes equations \cite{kawashima1984phd}, the system \eqref{51} has a unique solution $u^\tau_p=u^\tau_p(x,t)$ satisfying $u^\tau_p \in C([0,T],H^s)$. For $G_1\subset\subset G= \{(\rho, \rho v, c): \rho>0, \quad c< 2/3\}$, we define its maximum existence time as
\begin{eqnarray*}
  T^\tau :=\sup \{T>0 : u_p^\tau  \in C([0,T],H^s), u^\tau_p(x,t) \in G_1 \}.
\end{eqnarray*}
It can be shown as in \cite{yong2001basic} that
\begin{eqnarray*}
T^\tau > T_*,
\end{eqnarray*}
provided that, as $\tau$ tends to zero, the following error estimates
\begin{eqnarray*}
\sup_{x,t} |u_p^\tau(x,t) - u_0 (x, t) - \tau u_1(x,t)|=o(1), \\
\sup_t \| u_p^\tau(\cdot ,t) - u_0 (\cdot, t) - \tau u_1(\cdot, t) \|_{H^s} = O(1)
\end{eqnarray*}
hold for $t \in [0,\min\{T_*,T^\tau\})$. Thus it remains to prove the error estimate \eqref{eq:wcediff} with $T_*$ replaced by $\min\{T_*,T^\tau\}$.

For convenience, we will work with $w=(\rho,v)$, instead of $u=(\rho,\rho v)$, and  neglect the subscript $p$ to write $u^\tau_p$ as $u^\tau$. By the Sobolev calculus inequalities \cite{majda1984compressible}, the norms of $w$ are equivalent to those of $u$.

Set
\begin{eqnarray*}
  a(w) = \left( \begin{array}{cc} v & \rho \\ \frac{p_\rho}{\rho} & v \end{array} \right) \ \ \mbox{and} \ \
  a_0(w) = \left( \begin{array}{cc} \frac{p_\rho}{\rho^2} & 0 \\ 0 & 1 \end{array} \right).
\end{eqnarray*}
Note that $a_0(w)$ is symmetric positive definite for $\rho>0$ and $a_0(w)a(w)=a^T(w)a_0(w)$.
Then equation \eqref{51} can be rewritten as
\begin{eqnarray}\label{57}
  \partial_t w^\tau + a(w^\tau) \partial_x w^\tau = \left( \begin{array}{cc} 0 \\ \frac{4 \tau}{\rho^\tau} \partial^2_x v^\tau \end{array} \right) .
\end{eqnarray}

On the other hand, we deduce from \eqref{54} that $u_\tau \equiv u_0 +\tau u_1$ satisfies
\begin{eqnarray*}
  &&\partial_t u_\tau + f(u_\tau,0)_x \nonumber \\
  &=&  (f(u_\tau,0) - \tau f_u(u_0,0)u_1 - f(u_0,0))_x + \left( \begin{array}{c} 0 \\ 4 \tau \partial^2_x v_0 \end{array} \right) \nonumber \\
	&=& \left( \begin{array}{c} 0 \\ 4 \tau \partial^2_x v_\tau \end{array} \right)   + R
\end{eqnarray*}
with
$$
R=(f(u_\tau,0) - \tau f_u(u_0,0)u_1 - f(u_0,0))_x -\left( \begin{array}{c} 0 \\ 4 \tau^2 \partial^2_x v_1 \end{array} \right).
$$
Then it is not difficult to see that $w_\tau$ satisfies
\begin{eqnarray}\label{58}
  \partial_t w_\tau + a(w_\tau) \partial_x w_\tau = \left( \begin{array}{cc} 0 \\ \frac{4 \tau}{\rho_\tau} \partial^2_x v_\tau \end{array} \right) + \hat R
\end{eqnarray}
with
\begin{eqnarray*}
\hat{R} = \left( \begin{array}{cc} 1 & 0 \\ 0 & 1/\rho_\tau \end{array} \right)R .
\end{eqnarray*}
Obviously, we have $\|\hat{R}\|_{H^s} =O(\|R\|_{H^s})= O(\tau^2)$, for
\begin{eqnarray*}
  \|\partial^2_x v_1 \|_{H^s} &\le&  \|v_1\|_{H^{s+2}}
\end{eqnarray*}
and
\begin{eqnarray*}
  \|(f(u_\tau,0) &-& \tau f_u(u_0,0)u_1 - f(u_0,0))_x\|_{H^s} \\
  &=& \tau^2 \| u_1^Tf_{uu}(u_0+\tau \theta_2 \theta_1  u_1,0) \theta_1 u_1\|_{H^{s+1}} \\
  &\le&  C \tau^2 \|u_1\|_{H^{s+1}}^2 \|u_0+\tau \theta_2 \theta_1  u_1\|_{H^{s+1}},
\end{eqnarray*}
where $\theta_1,\theta_2 \in (0,1)$. Here we have used the Sobolev calculus inequalities \cite{majda1984compressible} and the fact that $u_0, u_1 \in H^{s+2}$.

Set $E = w^\tau - w_\tau$. It follows from \eqref{57} and \eqref{57} that
\begin{eqnarray*}
  \partial_t E + a(w^\tau) \partial_x E = (a(w_\tau) - a(w^\tau)) \partial_x w_\tau + \left( \begin{array}{cc} 0 \\ \frac{4\tau}{\rho^\tau} \partial^2_x v^\tau - \frac{4\tau}{\rho_\tau} \partial^2_x v_\tau \end{array} \right) - \hat{R}.
\end{eqnarray*}
This can be rewritten as
\begin{eqnarray*}
   \partial_t E + a(w^\tau) \partial_x E = (a(w_\tau) - a(w^\tau)) \partial_x w_\tau + \left( \begin{array}{cc} 0 \\ \frac{4\tau}{\rho^\tau} \partial^2_x (v^\tau - v_\tau) \end{array} \right) \\
   + \left( \begin{array}{cc} 0 \\ 4\tau(\frac{1}{\rho^\tau} -\frac{1}{ \rho_\tau})\partial^2_x v_\tau \end{array} \right)- \hat{R}.
\end{eqnarray*}
Taking the $l$-th order ($0 \le l \le s$) spatial derivatives leads to
\begin{eqnarray*}
  \partial_t \partial^l_x E + a(w^\tau) \partial^l_x E_x  = [a(w^\tau),\partial^l_x] E_x  + \left( \begin{array}{cc} 0 \\4\tau \partial^l_x(\frac{1}{\rho^\tau} \partial^2_x (v^\tau-v_\tau)) \end{array} \right) \\  + \left( \begin{array}{cc} 0 \\ 4 \tau \partial^l_x ((\frac{1}{\rho^\tau} - \frac{1}{\rho_\tau}) \partial^2_x v_\tau) \end{array} \right) -\partial^l_x \hat{R} + \partial^l_x ((a(w_\tau)-a(w^\tau))\partial_x w_\tau).
\end{eqnarray*}
We multiply the last equation with $\partial^l_x E^Ta_0(w^\tau)$ and integrate the resultant equation over $x$ to obtain
\begin{eqnarray}\label{58}
&& (a_0(w^\tau) \partial^l_x E,\partial^l_x E)_t + \int ( \partial^l_x E^T a_0(w^\tau) a(w^\tau) \partial^l_x E )_x dx \nonumber \\
&=&  ((a_0(w^\tau)_t + (a_0(w^\tau)a(w^\tau))_x) \partial^l_x E,\partial^l_x E)
+ 2(a_0(w^\tau)[a(w^\tau),\partial^l_x] E_x,\partial^l_x E)\nonumber \\
&& + 2 (4\tau \partial^l_x (\frac{1}{\rho^\tau} \partial^2_x (v^\tau-v_\tau)),\partial^l_x (v^\tau-v_\tau)) + 2(4\tau \partial^l_x ( (\frac{1}{\rho^\tau}-\frac{1}{\rho_\tau})\partial^2 v_\tau),\partial^l_x (v^\tau-v_\tau)) \nonumber\\
&& - 2(a_0(w^\tau)\partial^l_x\hat{R},\partial^l_x E)+ 2(a_0(w^\tau)\partial^l_x((a(w_\tau)-a(w^\tau))\partial_x w_\tau),\partial^l_x E) \nonumber \\
& \equiv& I_1 +I_2 +I_3 +I_4+I_5 + I_6.
\end{eqnarray}

Next we estimate the terms in the last equation. To do this, we notice that the second term on the left-hand side vanishes. Moreover, we recall that $w^\tau$ takes values in the compact set $G_1$ and $\|w_\tau(\cdot, t)\|_{H^{s+2}}$ is bounded uniformly with respect to $\tau$. Now, with the Sobolev inequalities \cite{majda1984compressible}, the terms $I_2, I_4, I_5$ and $I_6$ can be simply treated as follows
\begin{eqnarray*}
  I_2 &\le& 2 |a_0(w^\tau)|_{L^\infty} \|[a(w^\tau),\partial^l_x]E_x\|_{L^2} \|\partial^l_x E\|_{L^2} \nonumber \\
  &\le& C \|\partial^l_x E\|_{L^2} (|\partial_x a(w^\tau)|_{L^\infty}\|\partial^{s-1}_x E_x\|_{L^2} + |E_x|_{L^\infty} \|\partial^s_x a(w^\tau)\|_{L^2})  \nonumber \\
  &\le& C \|w^\tau\|_{H^s} \|E\|_{H^s}^2 \le C (1+\|E\|_{H^s}) \|E\|_{H^s}^2, \nonumber \\
  I_4 &\le&  C \tau \|\partial^l_x (v^\tau-v_\tau)\|_{L^2} \|\frac{1}{\rho^\tau}-\frac{1}{\rho_\tau}\|_{H^s} \|\partial^2_x v_\tau\|_{H^s}
  \le C \tau \|E\|_{H^s}^2, \nonumber\\
  I_5 &\le& C \|\partial^l_x \hat{R}\|_{L^2} \|\partial^l_x E\|_{L^2} \le C\tau^2\|\partial^l_x E\|_{L^2} \le C \tau^4 + C \|\partial^l_x E\|_{L^2}^2, \nonumber \\
  I_6 &\le& C\|\partial^l_x ((a(w_\tau)-a(w^\tau))\partial_x w_\tau)\|_{L^2} \|\partial^l_x E\|_{L^2}\nonumber\\
      &\le&  C \|w_\tau-w^\tau\|_{H^s} \|w_\tau\|_{H^{s+1}} \|\partial^l_x E\|_{L^2} \nonumber\\
      &\le&  C \|E\|_{H^s}^2. \label{515}
\end{eqnarray*}

For the first term, we deduce from equations in \eqref{51} that
\begin{eqnarray*}
  I_1 &\le&  |a_0(w^\tau)_t + (a_0(w^\tau) a(w^\tau))_x|_{L^\infty} \|\partial^l_x E\|_{L^2}^2 \nonumber\\
      &\le& C (|w^\tau_t|_{L^\infty} + |w^\tau_x|_{L^\infty}) \|\partial^l_x E\|_{L^2}^2 \nonumber\\
      &\le& C (|w^\tau_x|_{L^\infty} + \tau |\partial^2_x v^\tau|_{L^\infty}) \|\partial^l_x E\|_{L^2}^2 \nonumber\\
      &\le& C (\|w^\tau\|_{H^s} + \tau \|\partial_x(v^\tau-v_\tau)\|_{H^s} + \tau \|\partial_x v_\tau\|_{H^s} )\|\partial^l_x E\|_{L^2}^2 \nonumber\\
      &\le& C (\|w^\tau-w_\tau\|_{H^s}+\|w_\tau\|_{H^s}+\tau\|v_\tau\|_{H^{s+1}} + \tau \|\partial_x(v^\tau-v_\tau)\|_{H^s}) \|\partial^l_x E\|_{L^2}^2 \nonumber\\
      &\le& C (1+\|E\|_{H^s} + \tau \|\partial_x (v^\tau-v_\tau)\|_{H^s}) \|E\|_{H^s}^2. \label{516}
\end{eqnarray*}
The treatment of the third term $I_3$ needs integration by parts:
\begin{eqnarray*}
  I_3 &=& 8 \tau ([\partial^l_x,\frac{1}{\rho^\tau}] \partial^2_x(v^\tau-v_\tau) + \frac{1}{\rho^\tau} \partial^{l+2}_x(v^\tau-v_\tau),\partial^l_x (v^\tau-v_\tau) )\\
  &=& 8 \tau ([\partial^l_x,\frac{1}{\rho^\tau}] \partial^2_x(v^\tau-v_\tau),\partial^l_x (v^\tau-v_\tau))  -8 \tau(\partial_x (\frac{1}{\rho^\tau}) \partial^l_x(v^\tau-v_\tau),\partial^{l+1}_x (v^\tau-v_\tau)) \\ && -8\tau ( \frac{1}{\rho^\tau} \partial^{l+1}_x(v^\tau-v_\tau), \partial^{l+1}_x (v^\tau-v_\tau)) \\
  &\le& 8\tau \|[\partial^l_x,\frac{1}{\rho^\tau}]\partial^2_x(v^\tau-v_\tau)\|_{L^2} \|\partial^l_x (v^\tau-v_\tau)\|_{L^2} \\ & &+8\tau |\partial_x \frac{1}{\rho^\tau}|_{L^\infty} \|\partial^l_x (v^\tau-v_\tau)\|_{L^2} \|\partial^{l+1}_x(v^\tau-v_\tau)\|_{L^2}  -C_0 \tau \|\partial^{l+1}_x (v^\tau-v_\tau)\|_{L^2}^2\\
  &\le& C\tau \|\partial^l_x (v^\tau-v_\tau)\|_{L^2} (|\partial_x \frac{1}{\rho^\tau}|_{L^\infty} \|\partial_x^{s-1} \partial^2_x(v^\tau-v_\tau)\|_{L^2} + |\partial^2_x (v^\tau-v_\tau)|_{L^\infty} \|\partial^s_x \frac{1}{\rho^\tau}\|_{L^2})  \\ & & + C\tau \|\rho^\tau\|_{H^s} \|v^\tau-v_\tau\|_{H^s}\|\partial_x (v^\tau-v_\tau)\|_{H^s} -C_0 \tau\|\partial^{l+1}_x (v^\tau-v_\tau)\|_{L^2}^2\\
  &\le& C\tau (1+ \|E\|_{H^s})\|E\|_{H^s} \|\partial_x (v^\tau-v_\tau)\|_{H^s}-C_0 \tau \|\partial^{l+1}_x (v^\tau-v_\tau)\|_{L^2}^2 ,
\end{eqnarray*}
where $C_0 =\frac{ 8}{{\max_{x,t,\tau} \{\rho^\tau(x,t) \}}}$.

Combining \eqref{58} with the above estimates for the $I_k$'s and adding them together, we arrive at
\begin{eqnarray*}
 && \sum_{l=0}^s  (a_0(w^\tau) \partial^l_x E,\partial^l_x E)_t + C_0 \tau \|\partial_x (v^\tau-v_\tau)\|_{H^s}^2 \\
 &\le& C (1+\|E\|_{H^s})\|E\|_{H^s}^2 + C \tau(1+\|E\|_{H^s})\|E\|_{H^s} \|\partial_x(v^\tau-v_\tau)\|_{H^s} + C \tau^4  \\
 &\le& C (1+\|E\|_{H^s})\|E\|_{H^s}^2 + \frac{C_0\tau}{2} \|\partial_x(v^\tau-v_\tau)\|_{H^s}^2 + C \tau (1+\|E\|_{H^s})^2 \|E\|_{H^s}^2 + C \tau^4.
\end{eqnarray*}
Thus we have
\begin{eqnarray*}
  \sum_{l=0}^s  (a_0(w^\tau) \partial^l_x E,\partial^l_x E)_t + \frac{C_0}{2} \tau \|\partial_x (v^\tau-v_\tau)\|_{H^s}^2 \le   C (1+\|E\|_{H^s}^2)\|E\|_{H^s}^2 + C \tau^4.
\end{eqnarray*}
Recall that $a_0(w^\tau)$ is positive definite.
We integrate this inequality over $t \in [0,T]$ with $T \le \min \{T_*,T^\tau\}$ to obtain
\begin{eqnarray} \label{59}
 && \|E(T)\|_{H^s}^2 + \tau \int_0^T \|\partial_x(v^\tau(t)-v_\tau(t))\|_{H^s}^2 dt \nonumber \\
& \le &  C\int_0^T (1+\|E(t)\|_{H^s}^2)\|E(t)\|_{H^s}^2 dt +CT_* \tau^4.
\end{eqnarray}
Here we have used that $E(x, 0)=0$.

Set
\begin{eqnarray*}
  \phi(T) =  \int_0^T (1+\|E(t)\|_{H^s}^2)\|E(t)\|_{H^s}^2 dt + T_* \tau^4.
\end{eqnarray*}
It follows from \eqref{59} that
\begin{eqnarray*}
  \phi' \le C  \phi(1+C\phi)
\end{eqnarray*}
or
\begin{eqnarray*}
  -(\frac{1}{\phi})_t \le -C (-\frac{1}{\phi})+C^2.
\end{eqnarray*}
For this we use the Gronwall inequality to get
\begin{eqnarray*}
  \phi(T) \le \frac{e^{CT} \phi_0}{1-C e^{CT}  \phi_0}\le\frac{e^{CT_*} \phi_0}{1-C e^{CT_*} \phi_0} .
\end{eqnarray*}
Choosing $\tau$ sufficiently small such that $C e^{CT_*} \phi_0 \le \frac{1}{2}$ we arrive at
\begin{eqnarray*}
  \phi(T) \le 2T_*e^{CT_*}\tau^4.
\end{eqnarray*}
Hence we have
\begin{eqnarray*}
  \|E(T)\|_{H^s} \le C(T_*) \tau^2
\end{eqnarray*}
for $T \in [0,\min\{T_*,T^\tau\})$ and the proof is complete.
\end{proof}

\bibliography{Oldroydnew1}
\bibliographystyle{unsrt}

\end{document}





